Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd
Update paper

---
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism 
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
    - id: biosustain
      name: DTU
      department: DTU Biosustain
      city: Kongens Lyngby
      country: Denmark
  - name: "Nicholas Luke Cowie"
    affiliations: 
    - ref: biosustain
  - name: "Lars Keld Nielsen"
    affiliations: 
    - ref: biosustain
    - id: UQ
      name: The University of Queensland
      department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
      city: St Lucia
      country: Australia
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

>>>>

---
title: "Bayesian regression facilitates quantitative modelling of cell metabolism"
keywords: Bayesian inference, kinetic models of cell metabolism 
abstract: >
  This paper presents Maud, a command-line application that implements Bayesian
  statistical inference for kinetic models of biochemical metabolic reaction
  networks. Maud takes into account quantitative information from omics
  experiments and background knowledge, as well as structural information about
  kinetic mechanisms, regulatory interactions and enzyme knockouts. Our paper
  reviews the existing options in this area, presents a case study illustrating
  how Maud can be used to analyse a metabolic network and explains the
  biological, statistical and computational design decisions underpinning Maud.
number-sections: true
author: 
  - name: "Teddy Groves"
    orcid: 0000-0002-7109-3270
    email: tedgro@biosustain.dtu.dk
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      corresponding: true
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Nicholas Luke Cowie"
    affiliations: 
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
    attributes:
      equal-contributor: true
    note: These authors contributed equally to this research.
  - name: "Lars Keld Nielsen"
    affiliations: 
      - name: The University of Queensland
        department: Australian Institute for Bioengineering and Nanotechnology (AIBN)
        city: St Lucia
        country: Australia
      - id: biosustain
        name: DTU
        department: DTU Biosustain
        city: Kongens Lyngby
        country: Denmark
bibliography: bibliography.bib
format:
  acs-pdf:
    keep-tex: true
    journal:
      id: asbcd6  #This is an identifier for the target journal: from https://pubs.acs.org/, the identifier is the part of the URL after https://pubs.acs.org/journal/, e.g. for J. Org. Chem. it would be joceah.
      type: article  #article, note, communication, review, letter, or perspectivee
      layout: traditional #traditional or twocolumn, twocolumn currently broken for longtables
      hide-email: false # if enabled, hides email addresses (and fax/phone)
  acs-html:
   include-in-header: mathjax.html
   embed-resources: true
  docx: default
---

### 2023-10-31 paper/main.tex
Update paper

@@

\author{Lars Keld Nielsen}
\affiliation{DTU Biosustain, DTU, Kongens Lyngby, Denmark}
\affiliation{Australian Institute for Bioengineering and Nanotechnology
(AIBN), The University of Queensland, St Lucia, Australia}

@@

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, enhanced, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

>>>>

\altaffiliation{These authors contributed equally to this research.}

@@

\altaffiliation{These authors contributed equally to this research.}

\author{Lars Keld Nielsen}
\affiliation{Australian Institute for Bioengineering and Nanotechnology
(AIBN), The University of Queensland, St Lucia, Australia}
\affiliation{DTU Biosustain, DTU, Kongens Lyngby, Denmark}

@@

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi
